Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-10-22 refreport/response.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is the response to the referee's report for ApJ/ApJS manuscript
\#92163, ``Enzo: An Adaptive Mesh Refinement Code for Astrophysics,''
by the Enzo collaboration (Bryan et al.).  We thank the referee for
their feedback, and address each comment separately below.

\section{Test problems}

Regarding test problems, the referee's comment is:

\begin{verbatim}
However, the paper is let down due to the lack of tests presented for
many of the algorithms presented in the paper. In particular, the only
test presented for the MHD algorithm is the Orszag-Tang vortex test,
which 'does not seem to be extremely discriminating for MHD
algorithms' (Stone et al., 2008). In addition, results from some
tests, such as the photo-evaporation test, do not seem to be properly
compared to prior results in the literature (e.g. Jiang et
al. 2012). Finally, no tests appear to be presented for some tests
entirely, e.g. the Chemistry algorithms presented in Section 6.1.
\end{verbatim}

We have modified the test problem section as follows:

\begin{itemize}
\item \red{cooling Britton fill in here}
\item \red{radiation John fill in here}
\item \red{MHD Dave fill in here}
\end{itemize}

We also note that many of the fundamental \enzo\ algorithms are
extensively tested in separate method papers that focus on a single
algorithm/physics package, and a single test problem or small number
of test problems are included in the full \enzo\ method paper as a
demonstration that the algorithms behave sensibly.  In the subsection
describing these test problems, we cite the full method paper for the
appropriate algorithm and the direct the reader to it for more
information.  These additional algorithm method papers include ones
for both flavors of MHD contained in \enzo\ \citep{Wang:2009a,
Collins10}, the ray-tracing code \citep{Wise11_Moray}, and the
flux-limited diffusion \citep{ReynoldsHayesPaschosNorman2009}.

@@

\item The AREPO method paper \citep{2010MNRAS.401..791S} is 60 pages
long, covers a narrower range of topics, and the code is
closed-source.

\item The paper for the open-source Athena code
\citep{2008ApJS..178..137S} is 41 pages long, but only documents the
hydrodynamics and MHD algorithms.  At the time of the code's release,
this paper documented the entire feature set of the publicly-available
code.

\item The paper for the open-source ZEUS-MP 2 code
\citep{2006ApJS..165..188H} is 41 pages long, but again covers a
substantially narrower range of physics modules.  The entirety of the
publicly-available code is documented in this paper.
\end{itemize}

The only \textit{comparable} open-source code that we are aware of
whose method paper is broken up into multiple segments is the series
of three ZEUS-2D papers \citep{1992ApJS...80..753S,
1992ApJS...80..791S, 1992ApJS...80..819S}.  We argue, however, that
this is not a useful comparison, as the three papers were published in
the same issue of the Astrophysical Journal in 1992, and were
published back-to-back as consecutive articles in the same volume.  In
a time when the primary mode of consumption of articles was via paper
journals, this is effectively a single paper (with a length of
approximately 85 pages, no less).

### 2013-10-22 tests-photoevaporation.tex
Updating the photo-shadowing test to compare with the Iliev et al. (2009) paper.  Adding the PDF of temperature and Mach number and line cuts of density, temperature, pressure, and neutral fraction.

@@

The cloud is subject to radiation from a point source at the center of
the $x=0$ boundary with an ionizing photon luminosity $\dot{N}_\gamma
= 3 \times 10^{51}$ photons s$^{-1}$, corresponding to a flux $F_0 =
10^6 \unit{photons s}^{-1} \unit{cm}^{-2}$ at the clump surface
closest to the radiation source.  The radiation source has a spectrum
of a $T = 10^5 \unit{K}$ blackbody, and we use four energy groups with
the following mean energies and relative luminosities: $E_i = (17.98,
31.15, 49.09, 76.98) \unit{eV}, L_i/L = (0.23, 0.36, 0.24, 0.06)$ that
are optimized to reduce errors in the solutions with a full spectrum
and energy discretization \citep{Mirocha12}.  (Note that this choice
of energy groups is different from those used in Wise \& Abel 2011.)
\nocite{Wise11_Moray} We use a minimum angular resolution of 10 rays
per cell and a constant radiative transfer timestep of 25 kyr.  Figure
\ref{fig:shadowing} depicts the clump at $t = 15$ Myr with the outer
layers expanding after being photo-heated.  It also shows the sharp
shadowing effects of the dense clump in the neutral fraction plot that
is representative of ray tracing techniques.

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/code-test-shadowing.eps}
  \caption{Photo-evaporation of a dense clump using the Moray
ray-tracing module.  Clockwise from the upper left: slices
through the clump center of density, temperature, neutral hydrogen
fraction, and pressure at $t=15$~Myr after the initialization of the
simulation.  A point source of radiation is at the center of the -x
boundary and illuminates the clump with a constant luminosity, casting
a clear shadow behind the clump, as seen in the neutral hydrogen
fraction.}
  \label{fig:shadowing}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{figures/shadowing-rays.eps}
  \hfill
  \includegraphics[width=0.48\textwidth]{figures/shadowing-pdf.eps}
  \caption{Photo-evaporation of a dense clump using the Moray
    ray-tracing module.  Left panel: Line cuts in the axis from the
    point source to the clump center at $t = 1, 5, 10, 15$~Myr
    (clockwise from the upper-left side) of the density, temperature,
    pressure, and neutral fraction.  Right panel: Volume-weighted
    probability distribution functions for the temperature (left-hand
    panel) and flow Mach number (right-hand panel) at $t = 10
    \unit{Myr}$.}
  \label{fig:shadowing1}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=1.0\textwidth]{figures/shadowing-slices.eps}
  \caption{Photo-evaporation of a dense clump using the Moray
ray-tracing module.  Clockwise from the upper left: slices
through the clump center of density, temperature, neutral hydrogen
fraction, and pressure at $t=10$~Myr after the initialization of the
simulation.  A point source of radiation is at the center of the -x
boundary and illuminates the clump with a constant luminosity, casting
a clear shadow behind the clump, as seen in the neutral hydrogen
fraction.}
  \label{fig:shadowing2}
\end{figure}

@@

The cloud is subject to radiation from a point source at the center of
the $x=0$ boundary with an ionizing photon luminosity $\dot{N}_\gamma
= 3 \times 10^{51}$ photons s$^{-1}$, corresponding to a flux $F_0 =
10^6 \unit{photons s}^{-1} \unit{cm}^{-2}$ at the clump surface
closest to the radiation source.  The radiation source has a spectrum
of a $T = 10^5 \unit{K}$ blackbody, and we use four energy groups with
the following mean energies and relative luminosities: $E_i = (17.98,
31.15, 49.09, 76.98) \unit{eV}, L_i/L = (0.23, 0.36, 0.24, 0.06)$ that
are optimized to reduce errors in the solutions with a full spectrum
and energy discretization \citep{Mirocha12}.  (Note that this choice
of energy groups is different from those used in Wise \& Abel 2011.)
\nocite{Wise11_Moray} We use a minimum angular resolution of 10 rays
per cell and a constant radiative transfer timestep of 25 kyr.

The left panel in Figure \ref{fig:shadowing1} shows cuts of the
density, temperature, neutral fraction, and pressure in a line
connecting the source and the clump center at $t = 1, 5, 10, 15$~Myr.
At 1~Myr, the ionization front has propagated through the leftmost
500~pc of the clump.  This heated gas is now overpressurized, as seen
in the pressure plot of Figure \ref{fig:shadowing1} that expands into
the ambient medium.  This photo-evaporative flow becomes apparent at
5~Myr with the increased density and pressure on the left side of the
clump.  The right panel in Figure \ref{fig:shadowing1} shows the
volume-weighted distributions of the temperature and flow Mach number
in the entire domain at $t = 10 \unit{Myr}$.  Overall, our results
agree well with the codes presented in \citet{IlievEtAl2009} and the
uniform grid test of \moray~\citep{Wise11_Moray}.

However, there are some small differences in the line cuts and
distributions that arise from our choice of energy discretization that
better samples the high-energy tail of a $T = 10^5 \unit{K}$ blackbody
spectrum and does not signify possible shortcomings of \moray.  First,
in the temperature cut at $t = 10 \unit{Myr}$, the high-energy
radiation photo-heat the gas to $T = 10^4 \unit{K}$, but it remains
primarily neutral.  The temperature dip at $x \simeq 0.88$ is the gas
has not come into thermal equilibrium with the incident radiation.  A
stronger temperature dip exists in the \citeauthor{IlievEtAl2009}
results and varies from 1000 to 8000~K between codes.  Another minor
difference is the larger breadth in the temperature distribution
feature centered at $T = 4.5 \times 10^4 \unit{K}$ that corresponds to
the ambient medium.  This difference also originates from the
different sampling in the spectral energy distribution of the source.
Figure \ref{fig:shadowing2} depicts the same quantities in a
two-dimensional slice through the clump center at $t = 10$ Myr.  At
this time, it is apparent that the outer layers are expanding after
being photo-heated.  These slices also show the sharp shadowing
effects of the dense clump in the neutral fraction plot that is
representative of ray tracing techniques.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ms"
%%% End:
